State of the Art Review on Privacy-Preserving Authentication

### 2021-12-30 prism-backend/research/soa_review/app-ac.tex
Added comments of PrivacyPass and Whatsapp's DIT.

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
\end{itemize}

@@

\item Evernym. \url{https://www.evernym.com/}

@@

  \item {\bf Introduction}. Evernym is a software company that is some kind of
    relative of Sovrin. Their solution builds completely on the Sovrin system.

@@

>>>>

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
\item \cite{hkrw21}: multi-party revocation in Sovrin.
\end{itemize}

@@

\item Evernym and Sovrin. \url{https://www.evernym.com/}

@@

  \item {\bf Introduction}. Evernym is a software company that produced Sovrin.

@@

\item Hyperledger Fabric \& Idemix: \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html}.
  \item Hyperledger Fabric is the private and permissioned blockchain, initially
    created by IBM, and then used to seed the Hyperledger framework. Fabric's
    participants are authenticated via certificates issued by a Membership
    Service Provider (MSP) entity. In Fabric's first versions, the MSP was a
    conventional Certificate Authority (or a set of them, forming a traditional
    PKI system).
  \item Since v1.3, Fabric has included support for Idemix-based credentials
    \url{https://idemix.wordpress.com/}. Idemix credentials were initially based
    on CL signatures, but the current implementation seems to build on BBS+
    signatures\footnote{See \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html\#underlying-cryptographic-protocols}.}.    
    With Idemix-based credentials, users (including transactors of the system)
    can restrict the attributes that they share with verifiers, and their
    operations are anonymous and unlinkable (up to the revealed attributes). Not
    even the MSP can link them.
  \item An interesting practical aspect: the documentation advises to use at
    most one Idemix-based MSP per channel (or, per network). This is because
    the MDP identity is always revealed when showing a credential (as it is
    needed for verification). Therefore, the more MSPs, the easier it is to
    deanonymize users. They mention that it may be possible in the future to
    extend Idemix to support hierarchies of Idemix issuers and, therefore,
    provide more flexibility.
\item Hyperledger Indy, Aries, and Ursa:
  \item \url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/getting-started/indy-walkthrough.html}
  \item \url{https://www.hyperledger.org/use/aries}
  \item \url{https://github.com/hyperledger/ursa}
\item Indy is Hyperledger's project for digital identity. It was originated by
  the donation of the Sovrin codebase by Evernym, so the essentials explained
  for Sovrin mostly apply here too. It is therefore also based on CL anonymous
  credentials -- although, according to the online documentation%
  \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/hipe/en/latest/text/0109-anoncreds-protocol/README.html}.}%
  , it uses actual CL signatures (the original ones from 2002, based on RSA), as
  opposed to Evernym/Sovrin, that have migrated to the BBS+ equivalent.
\item In a nutshell, Indy covers layer 1 of the ToIP stack%
  \footnote{\url{https://trustoverip.org/}}, and Aries
  covers layers 2 and 3\footnote{According to this:
    \url{https://www.youtube.com/watch?v=FfuhlF9ZYPM}.}. This means that Indy
  manages DIDs \doubt{Does Indy also take care of writing credential schemas,
    etc. into the blockchain?}, and Aries uses the DIDs from Indy to establish
  secure connections and exchange verifiable credentials. Ursa is the
  cryptographic library that both projects use.
\item PrivacyPass \cite{dgs+18}.
  \item PrivacyPass is not an anonymous credential system per se, although
    probably some techniques can be leveraged. It is actually closer to
    Nymble, PEREA... and the line of anonymous blacklisting systems. Each
    time a user proves ``being human'', e.g., through a CAPTCHA, it gets
    $N$ blindly signed messages from a user, along with a batched
    zero-knowledge proof of knowledge of all of them being signed with the
    same secret key. To access a resource, the user then derives a MAC
    from the blindly signed value, and sends the result along with a tag
    that allows the server to reproduce the calculations and compare with
    the received MAC. If the comparison succeeds, the user is granted access.
    The server needs to keep a list of all used tags. Cryptographically, this
    is simple (and thus, it should be efficient). A main advantage seems to
    be that it is easily integrated in current web infrastructure. There is an
    open source implementation, avaliable in
    \url{https://privacypass.github.io/} that has been integrated in the
    Trust Token API \url{https://github.com/WICG/trust-token-api}.
\item Whatsapp's DIT (formerly known as Private Stats) \cite{hij+21}.
  Note: the report seems to have been taken offline. I managed to find a copy
  (I did not take note of the URL). The only available information seems
  to be this URL: \url{https://engineering.fb.com/2021/04/16/security/dit/}.
  \item This system is inspired by PrivacyPass, focusing on authentication of
    clients that need to log data in the context of Whatsapp -- hence,
    efficiency is very relevant. It indeed follows a similar execution flow to
    PrivacyPass: clients first authenticate against an authentication server,
    who requests to an anonymous credential server, on their behalf, a sort of
    anonymous credential using a blinded value received from the client. The
    received blinded credential is then unblinded, and can be used to authenticate
    subsequent ``anonymous connections''. Roughly, the anonymous credential is
    build from an attribute-based VOPRF inspired by Naor and Reingold
    \cite{nr04}. To authenticate a connection, similarly to PrivacyPass, the
    server recomputes a MAC, using as key a value reproduced through the VOPRF,
    using a tag that determines the attributes contained in the ``anonymous
    credential''. While the system seems very practical -- and indeed, its
    greatest merit is that it seems to be very well integrated in Whatsapp's
    infrastructure --, its relation to anonymous credentials is barely
    justifiable, despite it is mentioned several times in the paper. Its only
    common point is the support for different attributes. However multiple
    authentications with the same credential are linkable and, even though
    multiple attributes are supported, the client cannot choose which subset
    of the credentials are revealed. Moreover, security is defined for the
    VRF component, but no model or formalization whatsoever is given that
    resembles the usual ones for Anonymous Credentiasl (e.g., there is no
    property for unforgeability or anonymity of credentials).
